Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2019-12-24 ms/manuscript.Rmd
Exclude M. x maximum and revise MS with updated phylogenetic PCA results

Terrestrial and epiphytic species are partly differentiated in trait space, occupying mostly distinct areas but overlapping in the middle regardless of method used (standard or phylogenetic PCA) (\fig \@ref(fig:pca)*c*, *d*).
The first two PC axes explained `r percent(pca_std_cum_var)` and `r percent(pca_phy_cum_var)` of the variation in the trait data when analyzed using standard and phylogenetic PCA, respectively.
In the standard PCA, size-related traits tended to load on PC1, with SLA, number of pinnae pairs, and degree of dissection on PC2.
In the phylogenetic PCA, SLA was strongly loaded on PC1, while dissection, pinnae, and other size-related traits were mostly loaded on PC2.

@@

**\fig \@ref(fig:pca)**: Principal components analysis (PCA) of traits related to epiphytic growth in ferns from Moorea, French Polynesia. **(a, b)** PC loadings. **(c, d)** species scores. **(a)** and **(c)** are standard PCA, **(b)** and **(d)** are phylogenetic PCA. Epiphytes in green, terrestrial species in brown. Quantitative traits only, including only species with no missing observations for any traits ($\n = 104$ \si{\species}). Trait abbreviations as follows: dissection, degree of frond dissection; length, frond length; width, frond width; pinna, number of pinnae pairs; rhizome, rhizome diameter; stipe, stipe length; SLA, specific leaf area.

>>>>

Terrestrial and epiphytic species are partly differentiated in trait space, occupying mostly distinct areas but overlapping in the middle regardless of method used (standard or phylogenetic PCA) (\fig \@ref(fig:pca)*c*, *d*).
The first two PC axes explained `r percent(pca_std_cum_var)` and `r percent(pca_phy_cum_var)` of the variation in the trait data when analyzed using standard and phylogenetic PCA, respectively.
In the standard PCA, size-related traits tended to load on PC1, with SLA, number of pinnae pairs, and degree of dissection on PC2.
Loadings in the phylogenetic PCA are similar but approximately reversed relative to the standard PCA.

@@

**\fig \@ref(fig:pca)**: Principal components analysis (PCA) of traits related to epiphytic growth in ferns from Moorea, French Polynesia. **(a, b)** PC loadings. **(c, d)** species scores. **(a)** and **(c)** are standard PCA, **(b)** and **(d)** are phylogenetic PCA. Epiphytes in green, terrestrial species in brown. Quantitative traits only, including only species with no missing observations for any traits (\n = `r pca_results[["species_locs"]] %>% pull(species) %>% n_distinct` \si{\species}). Trait abbreviations as follows: dissection, degree of frond dissection; length, frond length; width, frond width; pinna, number of pinnae pairs; rhizome, rhizome diameter; stipe, stipe length; SLA, specific leaf area.
